Estimating the incidence of SARS-CoV-2 from prevalence data

### 2023-09-28 incidence-prevalence.tex
AIDS intro and refs

\emph{Backcalculation} is the procedure for estimating incidence based on a measurement of prevalence.
It was first developed in the context of HIV (human immunodeficiency virus) and AIDS (acquired immune deficiency syndrome)~\autocite{brookmeyerMethod}.
HIV is a virus transmitted sexually or through blood, and causes the disease AIDS.
AIDS has killed around 40 million people; at its peak, around 2 million people died from AIDS each year\todo{cite WHO}.
In this context, backcalculation estimates the incidence of HIV infection from data on the number of AIDS diagnoses and the distribution of the time between infection and AIDS diagnosis~\autocite{brookmeyerBackcalculation}{brookmeyerMeasuring}.
\todo{explain how AIDS diagnosis is "prevalence" data (is it?)}

Two processes are involved in backcalculation: the \emph{prevalence process} and the \emph{observation process}.
The prevalence process describes the relationship between incidence and prevalence.
The observation process describes the relationship between prevalence and the observed data.

>>>>

\emph{Backcalculation} is the procedure for estimating incidence based on a measurement of prevalence.
It was first developed in the context of HIV (human immunodeficiency virus) and AIDS (acquired immune deficiency syndrome)~\autocite{brookmeyerMethod}.
HIV is a virus transmitted sexually or through blood, and causes the disease AIDS.
AIDS has killed around 40 million people; at its peak, around 2 million people died from AIDS each year~\autocite{unaids2023}.
In this context, backcalculation estimates the incidence of HIV infection from data on the number of AIDS diagnoses and the distribution of the time between infection and AIDS diagnosis~\autocites{brookmeyerBackcalculation}{brookmeyerMeasuring}.
\todo{explain how AIDS diagnosis is "prevalence" data (is it?)}

Three processes are involved in backcalculation: the \emph{infection process}, the \emph{prevalence process} and the \emph{observation process}.
The infection process describes how individuals become infected.
The prevalence process describes the relationship between incidence and prevalence.
The observation process describes the relationship between prevalence and the observed data.
